---
title: "The effect of aperture size on contrast in SHeM"
author: "Sam Lambrick"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook: 
    toc: true
    number_sections: true
    theme: paper
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)  # We are working in the tidyverse
library(pracma)     # Numerical/mathmatical functions, 'practical math'
library(magrittr)   # Some more usefull tidyverse things, e.g. '%<>%'
library(tikzDevice) # Output graphics to TikZ for inclusion in LaTeX
library(ggthemes)   # Additional themes for ggplot, has solarized colour scheme
                    # for discrete plots
library(viridis)    # Good continous colour scheme
library("heliumApertureIntensity")
```


# Analysis functions

```{r}
# Get the standard deviation from the other data
sigma_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["sigma"]]
sigma_calc <- Vectorize(sigma_calc, vectorize.args = "beta_v")

# Get the mean of the absolute value of 
diff_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["diff"]]
diff_calc <- Vectorize(diff_calc, vectorize.args = "beta_v")

# Get the average from the other data
av_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["av"]]
av_calc <- Vectorize(av_calc, vectorize.args = "beta_v")
```


# Parameters

Define the range of angles to consider. The range of half cone angles is
$0 < \beta <= 90$. The range of angles between the normal of the surface element
and the centre of the detector aperture is $0 < \varpsi <= 180$.

```{r}
# Range of psis (angle of the surface to the aperture)
psi_range <- c(0, 90 + 90)

# Range of betas (half cone angle of aperture)
beta_range <- c(0, 90)

# The distance from the sample to the aperture, defines the area, mm^2, of the
# aperture and thus the pumping from the stagnation region back to the sample
# chamber. In mm.
working_dists <- seq(0.1, 5, by = 0.05)

# The present half cone angle
present_half_cone <- 10

# The present working distance
present_working_dist <- 3
```


# Signal level with aperture size/placement


## Create data

Create a data frmae for all values of $\psi$ and $\varphi$, then calculate the
detected signal level for those parameters.

```{r}
# Range of beta
betas <- seq(beta_range[1], beta_range[2], by = 1)

# Range of psi
psis <- seq(psi_range[1], psi_range[2], by = 1)

# Overall data frame
df_signal <- tibble(beta = NA, I = NA, psi = NA)

for (i in seq(1, length(betas))) {
    Is <- rep(0, length(psis))
    for (j in seq(1, length(psis))) {
        Is[j] <- intensityCircular(psis[j]*pi/180, betas[i]*pi/180)
    }
    df_signal <- bind_rows(df_signal, tibble(psi = psis, beta = betas[i], I = Is))
}

# Remove the first row that are NA's
df_signal <- df_signal[-1,]

# Normalise the signals such that 1 corresponds to a 45deg surface angle and a
# 5deg half cone angle, i.e. the current level of signal
N <- df_signal %>% filter(beta == 5, psi == 45)
df_signal %<>% mutate(I = I/N[["I"]])

# Save the basic data frame to a text file
df_signal %>% write_csv("aperture_signal_data.csv")
```

As the calculation takes a minute an alternative is to import previously
calculated data.

```{r}
df_signal <- read_csv("aperture_signal_data.csv", show_col_types = FALSE)
```


## Singnal plots

Create contour plots of the signal level and the signal to noise ratio. The
signal to noise ratio will be the $\propto \sqrt{I}$ because the dominant form
of noise is shot noise.

```{r, fig.width=2.354, fig.height=5}
df_signal %<>% mutate(SNR = sqrt(I))
df_signal %<>% mutate(SNR = if_else(is.nan(SNR), 0, SNR))

# Plot of the signal as a contour plot and heatmap
plt_contour <- df_signal %>%
    ggplot(aes(x = beta, y = psi)) +
    geom_raster(aes(fill = I), interpolate = TRUE) +
    geom_contour(aes(z = I), colour = "white", size = 0.5, binwidth = 10) +
    geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
    scale_fill_viridis() +
    scale_x_continuous(breaks = c(0,20,40,60,80,90)) +
    scale_y_continuous(breaks = c(0,20,40,60,80,100,120,140,160,180)) +
    coord_fixed(expand = FALSE) + 
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(expression("Surface angle/"*degree)) +
    labs(fill = "Signal") + 
    theme(text = element_text(size = 9), legend.position = "top")

print(plt_contour)
```

```{r, fig.width=2.354, fig.height=5}
# Plot of the signal to noise ratio as a contour plot and heatmap
plt_contour_SNR <- df_signal %>%
    ggplot(aes(x = beta, y = psi)) +
    geom_raster(aes(fill = SNR), interpolate = TRUE) +
    geom_contour(aes(z = SNR), colour = "white", size = 0.5, binwidth = 1) +
    geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
    scale_fill_viridis() +
    scale_x_continuous(breaks = c(0,20,40,60,80,90)) +
    scale_y_continuous(breaks = c(0,20,40,60,80,100,120,140,160,180)) +
    coord_fixed(expand = FALSE) + 
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(expression("Surface angle/"*degree)) +
    labs(fill = "SNR") + 
    theme(text = element_text(size = 9), legend.position = "top")

print(plt_contour_SNR)
```

Create a plot of the detected intensity with aperture size using aperture radius
instead of half cone angle. Assume a working distance of 3mm and a detection
angle of $45^\circ$.

```{r, fig.width=3, fig.height=2}
rs = seq(0, 2, by = 0.1)
I <- rep(0, length(rs))
for (i in seq(1, length(rs))) {
    I[i] = intensityRadius(45*pi/180, rs[i], 3)
}
I <- I/intensityRadius(45*pi/180, 0.5, 3)
df_signal2 <- tibble(rs, I)

plt_radius <- df_signal2 %>% ggplot(aes(x = rs, y = I)) +
    geom_line() + 
    geom_vline(aes(xintercept = 0.5), colour = colorblind_pal()(2)[2]) + 
    labs(x = "Aperture radius/mm", y = "Signal") + 
    theme(text = element_text(size = 9))

print(plt_radius)
```

### Save the plots

Save the contour plots as vector graphics (`.eps`) and as raster graphics (`.png`).

```{r}
ggsave("signal_aperture.eps", plt_contour, width = 2.354, height = 5)
ggsave("SNR_aperture.eps", plt_contour_SNR, width = 2.354, height = 5)

ggsave("signal_aperture.png", plt_contour, width = 2.354, height = 5)
ggsave("SNR_aperture.png", plt_contour_SNR, width = 2.354, height = 5)

ggsave("signal_aperture_mm.eps", plt_radius, width = 3, height = 2)
ggsave("signal_aperture_mm.png", plt_radius, width = 3, height = 2)
```

Export the contour plots as `.tex` files for improting into my thesis.

```{r message=FALSE, warning=FALSE}
plt_contour <- plt_contour + 
    xlab("Half cone angle/$^\\circ$") +
    ylab("Surface angle/$^\\circ$") +
    theme(text = element_text(size = 9))
tikz("2Dplot.tex", standAlone = FALSE, width = 2.354, height = 5)
print(plt_contour)
dev.off()
    
plt_contour_SNR <- plt_contour_SNR + 
    xlab("Half cone angle/$^\\circ$") +
    ylab("Surface angle/$^\\circ$") +
    theme(text = element_text(size = 9))
tikz("2Dplot_SNR.tex", standAlone = FALSE, width = 2.354, height = 5)
print(plt_contour_SNR)
dev.off()

tikz("signal_aperture_mm.tex", standAlone = FALSE, width = 3, height = 2)
print(plt_radius)
dev.off()
```


# Elliptical aperture

Is it better to have a circular aperture or an elliptical one. If an elliptical
one is a 'wide' or 'long' aperture better?

Use the ellipse integration to find out.


## Test the elliptical integral

First test the elliptical integral against the circular analytic formula to
check that it's working

```{r, fig.width=5, fig.height=3}
betas <- seq(1, 20)
I_circ <- rep(0, length(betas))
I_ellip <- rep(0, length(betas))
for (i in seq(1, length(betas))){ 
    I_circ[i] <- intensityAnl(45*pi/180, betas[i]*pi/180)
    I_ellip[i] <- intensityElliptical(45*pi/180, betas[i]*pi/180, betas[i]*pi/180)
}

df_ellipTest <- tibble(betas, I_circ, I_ellip)

plt_test <- df_ellipTest %>% pivot_longer(!betas, names_to = "Model", values_to = "I") %>% 
    ggplot(aes(x = betas, y = I, linetype = Model, colour = Model)) + 
    geom_line() + 
    scale_color_colorblind() + 
    theme(text = element_text(size = 9))

print(plt_test)
```


## Solid angle calculations

In order to compare contrast between the elliptical and circular shaped
apertures it is necessary to get an equivalence in solid angle for the whole
range of values. Do the calculation both for an aperture with the same solid
angle as the current design and one with double the solid angle.

```{r}
# Current solid angle
current_omega <- omegaEllipseBeta(10*pi/180, 10*pi/180)

# Range of angles in one of the dimensions
beta_a <- c(1.5, 2.5, 5, 10)

# Calculate the  values of the other half cone angle
beta_b <- rep(0, length(beta_a))
for (i in seq(1, length(beta_a))) {
    beta_tmp <- seq(1, 89, by=0.2)
    omegas <- rep(0, length(beta_tmp))
    for (j in seq(1, length(beta_tmp))) {
        omegas[j] <- omegaEllipseBeta(beta_a[i]*pi/180, beta_tmp[j]*pi/180)
    }
    tmp_fun <- approxfun(omegas, beta_tmp)
    beta_b[i] <- tmp_fun(current_omega)
}
```

```{r}
# Check the solid angles calculated
omegas <- rep(0, length(beta_a))
for (i in seq(1, length(beta_a))) {
    omegas[i] <- omegaEllipseBeta(beta_a[i]*pi/180, beta_b[i]*pi/180)
}
print("Fractional range of the resulting values:")
print(diff(range(omegas))/mean(omegas))

```

For a few specific ratios look at how the signal changes with the surface
orientation.

```{r, fig.width=2.354, fig.height=2.6, warning=FALSE}
df_elliptical <- tibble(beta_a=NA, beta_b=NA, psi=NA, I=NA)
psis <- seq(0, 90)
for (i in seq(1, length(beta_a))) {
    Is <- rep(0, length(psis))
    for (j in seq(1, length(Is))) {
        Is[j] <- intensityElliptical(psis[j]*pi/180, beta_a[i]*pi/180, beta_b[i]*pi/180)
    }
    df_elliptical <- bind_rows(df_elliptical, tibble(psi=psis, beta_a=beta_a[i], 
                                                     beta_b=beta_b[i], I = Is))
}

# Remove the first row that are NA's
df_elliptical <- df_elliptical[-1,]

df_elliptical %<>% mutate(aspect_ratio = beta_b/beta_a)

plt_elliptical <- df_elliptical %>% 
    mutate(aspect_ratio = as_factor(round(df_elliptical$aspect_ratio)),
           I = I/max(I)) %>%
    ggplot(aes(x = psi, y = I, colour = aspect_ratio))  + 
    geom_line() + 
    scale_color_colorblind() +
    labs(x = "$\\psi^\\circ$", y = "Relative signal") + 
    guides(colour=guide_legend(nrow=1)) +
    scale_x_continuous(breaks = c(0,20,40,60,80,90))
    xlim(0, 90) +
    ylim(c(0, 1)) +
    theme(legend.position = "top", 
          legend.title = element_blank(), 
          text = element_text(size = 9))

print(plt_elliptical)
```

## Partial masking with an elliptical detector

If there is partial masking then a Monte-Carlo method of integration has to be
used.

### MC test

```{r}
psi <- seq(0, 110)
I <- rep(0, length(psi))
IMC <- rep(0, length(psi))
for (i in seq(1, length(psi))) {
    I[i] <- intensityElliptical(psi[i]*pi/180, 10*pi/180, 10*pi/180)
    IMC[i] <- intensityEllipticalMC(psi[i]*pi/180, 10*pi/180, 10*pi/180, 300000)
}
df_elliptical <- tibble(psi=psi, Int=I/max(I), MC=IMC/max(IMC))
```

```{r}
df_elliptical %>% pivot_longer(!psi, names_to = "Model", values_to = "signal") %>%
    ggplot(aes(x=psi, y=signal, colour=Model)) + 
    geom_line() + 
    scale_colour_colorblind() +
    ylim(0, 1)
```

The test shows that the models agree. Now 

```{r}
df_elliptical2 <- tibble(beta_a=NA, beta_b=NA, psi=NA, I=NA)
psis <- seq(0, 135, by=1.5)
for (i in seq(1, length(beta_a))) {
    Is <- rep(0, length(psis))
    for (j in seq(1, length(Is))) {
        Is[j] <- intensityEllipticalMC(psis[j]*pi/180, beta_b[i]*pi/180, beta_a[i]*pi/180, 10000000)
    }
    df_elliptical2 <- bind_rows(df_elliptical2, tibble(psi=psis, beta_a=beta_a[i], 
                                                     beta_b=beta_b[i], I = Is))
}

# Remove the first row that are NA's
df_elliptical2 <- df_elliptical2[-1,]

df_elliptical2 %<>% mutate(aspect_ratio = beta_b/beta_a)

df_elliptical2 %>% write_csv("elliptical_long_data.csv")
```

Alternativly load the data from a data file because the computation takes time.

```{r}
df_elliptical2 <- read_csv("elliptical_long_data.csv")
```

```{r, fig.width=2.354, fig.height=2.6}
plt_elliptical2 <- df_elliptical2 %>% 
    mutate(aspect_ratio = as_factor(round(aspect_ratio)),
           I = I/max(I)) %>%
    ggplot(aes(x = psi, y = I, colour = aspect_ratio))  + 
    #geom_line() + 
    geom_smooth(method = "loess", se=FALSE, span=0.2) + 
    scale_colour_colorblind() +
    labs(x = "\\psi/^\\circ", y = "Relative signal") +
    ylim(c(0, 1)) +
    theme(legend.position = "top", 
          legend.title = element_blank(), 
          text = element_text(size = 9))

print(plt_elliptical2)
```

## Save elliptical plots

There are two plots, one for "wide" apertures and the other for "long"
apertures.

# Analyse contrast

Caculate both the RMS contrast to noise and the differential contrast to noise
for each value of beta

```{r}
# Calculate the standard deviation contrast and noise for each value of beta
df_sigma <- tibble(beta = NA, contrast = NA, av = NA)
df_diff <- tibble(beta = NA, contrast = NA, av = NA)
for (i in seq(1, length(betas))) {
    df_oneBeta <- df_signal %>% filter(beta == betas[i], psi <= beta + 90)
    sig <- sd(df_oneBeta[["I"]])
    dif <- mean(abs(diff(df_oneBeta[["I"]])))
    av <- mean(df_oneBeta[["I"]])
    df_sigma %<>% add_row(beta = betas[i], contrast = sig, av = av)
    df_diff %<>% add_row(beta = betas[i], contrast = dif, av = av)
}
df_sigma <- df_sigma[-1,]
df_diff <- df_diff[-1,]

# RMS and differential contrast to noise
df_sigma %<>% mutate(CNR = contrast/sqrt(av))
df_diff %<>% mutate(CNR = contrast/sqrt(av))

# Normalise such that a value of 1 is the present aperture size
N1 <- (df_sigma %>% filter(beta == present_half_cone))[["CNR"]]
N2 <- (df_diff %>% filter(beta == present_half_cone))[["CNR"]]
df_sigma %<>% mutate(CNR = CNR/N1)
df_diff %<>% mutate(CNR = CNR/N2)

# Normalise the contrast too
N1 <- (df_sigma %>% filter(beta == present_half_cone))[["contrast"]]
N2 <- (df_diff %>% filter(beta == present_half_cone))[["contrast"]]
df_sigma %<>% mutate(contrast = contrast/N1)
df_diff %<>% mutate(contrast = contrast/N2)

# Combine the RMS and differential contrast to noise
df_contrast <- bind_rows("sigma" = df_sigma, "diff" = df_diff, .id = "method")

# Add the equivalent signal increase
df_contrast %<>% mutate(signal_increase = CNR^2)

# Calculate the Contrast to noise and difference to noise between 0/45, 0/90, 
# 45/90, for each beta
df_difference <- tibble(beta = NA, CNR = NA, I_0_45 = NA, I_0_90 = NA, 
                        I_45_90 = NA)
for (i in seq(1, length(betas))) {
    df_oneBeta <- df_signal %>% filter(beta == betas[i])
    I_0 <- (df_oneBeta %>% filter(psi == 0))[["I"]]
    I_45 <- (df_oneBeta %>% filter(psi == 45))[["I"]]
    I_90 <- (df_oneBeta %>% filter(psi == 90))[["I"]]
    df_difference %<>% add_row(beta = betas[i], CNR = "Difference", 
                               I_0_45 = I_0 - I_45,
                               I_0_90 = I_0 - I_90,
                               I_45_90 = I_45 - I_90)
    df_difference %<>% add_row(beta = betas[i], CNR = "DNR", 
                               I_0_45 = diffNoise(I_0, I_45),
                               I_0_90 = diffNoise(I_0, I_90),
                               I_45_90 = diffNoise(I_45, I_90))
}
df_difference <- df_difference[-1,]

# Normalise so that the current set up at a surface of 45deg has a value of 1
# for the difference between 0/45
N1 <- (df_difference %>% filter(beta == present_half_cone, 
                                CNR == "Difference"))[["I_0_45"]]
N2 <- (df_difference %>% filter(beta == present_half_cone, 
                                CNR == "DNR"))[["I_0_45"]]
df_difference %<>% mutate(
    I_0_45 = if_else(CNR == "Difference", I_0_45/N1, I_0_45/N2),
    I_0_90 = if_else(CNR == "Difference", I_0_90/N1, I_0_90/N2),
    I_45_90 = if_else(CNR == "Difference", I_45_90/N1, I_45_90/N2)
)
```

#--------------------------------- Pumping ------------------------------------#

```{r}
# # Data frame
# df_pumping <- tibble(beta = rep(betas, times = length(working_dists)),
#                      working_dist = rep(working_dists, each = length(betas)))
# 
# # Calculate the pumping for each 
# df_pumping %<>% mutate(pumping = conductance_ap(beta, working_dist))
#                      
# # Calculate the standard deviation and the RMS contrast to noise
# df_pumping %<>% mutate(
#     sigma = df_contrast %>% sigma_calc(beta),
#     av = df_contrast %>% av_calc(beta)
# )
# df_pumping %<>% mutate(
#     sigma = sigma*pump_ion/(pump_ion + pumping),
#     av = av*pump_ion/(pump_ion + pumping),
#     CNR_sigma = sigma/sqrt(av)
# )
# 
# # Normalise such that a value of 1 is the present aperture size
# N <- (df_pumping %>% filter(beta == present_half_cone, 
#     abs(working_dist - present_working_dist) < 0.0001))[["CNR_sigma"]]
# df_pumping %<>% mutate(CNR_sigma = CNR_sigma/N)
# 
# # Add the equivalent signal increase
# df_pumping %<>% mutate(signal_increase = CNR_sigma^2)
```

#----------------------------------- Plot -------------------------------------#

```{r}

# Plot of the RMS contrst to noise and the standard deviation
facet_names <- c(
    'CNR'="Contrast to noise",
    'contrast'="Contrast"
)
leg_labs <- list(
    'sigma'="RMS",
    'diff'="Differential"
)
plt_CNR_sig <- df_contrast %>%
    gather(key = "variable", value = "value", -beta, -av, -method, -signal_increase) %>%
    ggplot(aes(x = beta, y = value, colour = method)) +
    geom_line() + 
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    scale_colour_manual(values = colorRampPalette(solarized_pal()(8))(2),
                        labels = leg_labs)  +
    facet_wrap( ~ variable, ncol = 2, scale = "free_y", 
               labeller = as_labeller(facet_names)) +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(NULL) +
    theme(aspect.ratio = 2/(1+sqrt(5)), legend.title = element_blank())

print(plt_CNR_sig)

# Plot the required signal increase
plt_signal_increase <- df_contrast %>%
    ggplot(aes(x = beta, y = signal_increase, colour = method)) +
    geom_line() + 
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    scale_colour_manual(values = colorRampPalette(solarized_pal()(8))(2),
                        labels = leg_labs)  +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab("Equivalent overall signal increase") +
    theme(aspect.ratio = 2/(1+sqrt(5)), legend.title = element_blank())

print(plt_signal_increase)

# Plot the difference to noise and the difference
leg_labs <- list(
    bquote(0^degree * "," ~ 45^degree), 
    bquote(0^degree * "," ~ 90^degree),
    bquote(45^degree * "," ~ 90^degree)
)
plt_CNR_diff <- df_difference %>%
    gather(key = "pair", value = "value", -beta, -CNR) %>%
    ggplot(aes(x = beta, y = value, colour = pair)) + 
    geom_line() +
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
#    scale_colour_manual(values = colorRampPalette(solarized_pal()(8))(3), 
#                        labels = leg_labs)  +
    facet_wrap( ~ CNR, ncol = 2, scale = "free_y") +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(NULL) +
    theme(legend.title = element_blank()) +
    theme(aspect.ratio = 2/(1+sqrt(5)))
```

```{r}
# Plot of the contrast to noise with the pumping taken into account
#facet_names <- c(
#    'CNR_sigma'="RMS contrast to noise",
#    'sigma'="Standard deviation"
#)
#plt_CNR_pumping <- df_pumping %>%
#    filter(working_dist == 3) %>%
#    gather(key = "variable", value = "value", -beta, -av, -signal_increase) %>%
#    ggplot(aes(x = beta, y = value)) +
#    geom_line(colour = colorRampPalette(solarized_pal()(8))(1)) + 
#    geom_vline(aes(xintercept = present_half_cone)) +
#    scale_x_continuous(breaks = c(0,20,40,60,80)) +
#    facet_wrap( ~ variable, ncol = 2, scale = "free_y", labeller = as_labeller(facet_names)) +
#    xlab(expression("Half cone angle/"*degree)) + 
#    ylab(NULL) +
#    theme(aspect.ratio = 2/(1+sqrt(5)))

# # Plot the equivalent signal increase
# plt_signal_increase_pumping <- df_pumping %>%
#     filter(working_dist == 3) %>%
#     ggplot(aes(x = beta, y = signal_increase)) +
#     geom_line(colour = colorRampPalette(solarized_pal()(8))(1)) + 
#     geom_vline(aes(xintercept = present_half_cone)) +
#     scale_x_continuous(breaks = c(0,20,40,60,80)) +
#     xlab(expression("Half cone angle/"*degree)) + 
#     ylab("Equivalent overall signal increase") +
#     theme(aspect.ratio = 2/(1+sqrt(5)))
# 
#     
# # Remove the NaNs for plotting
# df_pumping[is.na(df_pumping)] <- 0
# 
# # Plot of the signal improvment as a function of both half cone angle and the
# # working distance.
# plt_contour_pumping <- df_pumping %>%
#     ggplot(aes(x = beta, y = working_dist)) +
#     geom_raster(aes(fill = signal_increase), interpolate = TRUE) +
# #    geom_contour(aes(z = signal_increase), colour = "white", size = 0.5, binwidth=1) +
#     geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
#     geom_hline(aes(yintercept = present_working_dist), colour = "firebrick1") +
#     scale_fill_viridis() +
#     coord_cartesian(expand = FALSE) + 
#     xlab(expression("Half cone angle/"*degree)) + 
#     ylab(expression("Working distance/mm")) +
#     labs(fill = "Equivalent signal\nincrease")
# 
# # Plot of the RMS CNR as a function of both half cone angle and the
# # working distance.
# plt_contour_pumpingCNR <- df_pumping %>%
#     ggplot(aes(x = beta, y = working_dist)) +
#     geom_raster(aes(fill = CNR_sigma), interpolate = TRUE) +
#     geom_contour(aes(z = CNR_sigma), colour = "white", size = 0.5, binwidth=1) +
#     geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
#     geom_hline(aes(yintercept = present_working_dist), colour = "firebrick1") +
#     scale_fill_viridis() +
#     coord_cartesian(expand = FALSE) + 
#     xlab(expression("Half cone angle/"*degree)) + 
#     ylab(expression("Working distance/mm")) +
#     labs(fill = "CNR")
```


