---
title: "The effect of aperture size on contrast in SHeM"
author: "Sam Lambrick"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_notebook: 
    toc: true
    number_sections: true
    theme: paper
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)  # We are working in the tidyverse
library(pracma)     # Numerical/mathmatical functions, 'practical math'
library(magrittr)   # Some more usefull tidyverse things, e.g. '%<>%'
library(tikzDevice) # Output graphics to TikZ for inclusion in LaTeX
library(ggthemes)   # Additional themes for ggplot, has solarized colour scheme
                    # for discrete plots
library(viridis)    # Good continous colour scheme
library(devtools)
load_all("../heliumApertureIntensity")
```


# Analysis functions

These functions are not used apart from in the pumping section, and they don't
seem to do much.

```{r}
# Get the standard deviation from the other data
sigma_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["sigma"]]
sigma_calc <- Vectorize(sigma_calc, vectorize.args = "beta_v")

# Get the mean of the absolute value of 
diff_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["diff"]]
diff_calc <- Vectorize(diff_calc, vectorize.args = "beta_v")

# Get the average from the other data
av_calc <- function(signals, beta_v) (signals %>% filter(beta == beta_v))[["av"]]
av_calc <- Vectorize(av_calc, vectorize.args = "beta_v")
```


# Parameters

Define the range of angles to consider. The range of half cone angles is
$0 < \beta <= 90$. The range of angles between the normal of the surface element
and the centre of the detector aperture is $0 < \varpsi <= 180$.

```{r}
# Range of psis (angle of the surface to the aperture)
psi_range <- c(0, 90 + 90)

# Range of betas (half cone angle of aperture)
beta_range <- c(0, 90)

# The distance from the sample to the aperture, defines the area, mm^2, of the
# aperture and thus the pumping from the stagnation region back to the sample
# chamber. In mm.
working_dists <- seq(0.1, 5, by = 0.05)

# The present half cone angle
present_half_cone <- 10

# The present working distance
present_working_dist <- 3

# Do saving to .tex files
save_tex <- FALSE
# Do saving to .eps/.pdf files
save_plots <- FALSE
```


# Signal level with aperture size/placement


## Create data

Create a data frmae for all values of $\psi$ and $\varphi$, then calculate the
detected signal level for those parameters. The signal levels are normalised
such that a 45deg surface angle and 5deg half cone angle is equal to 1.

If the data has previously been calculated it can be imported instead.

```{r}
if (FALSE) {
    # Range of beta
    betas <- seq(beta_range[1], beta_range[2], by = 1)
    
    # Range of psi
    psis <- seq(psi_range[1], psi_range[2], by = 1 )
    
    # Overall data frame
    df_signal <- tibble(beta = NA, I = NA, psi = NA)
    
    for (i in seq(1, length(betas))) {
        Is <- rep(0, length(psis))
        for (j in seq(1, length(psis))) {
            Is[j] <- intensityCircular(psis[j]*pi/180, betas[i]*pi/180)
        }
        df_signal <- bind_rows(df_signal, tibble(psi = psis, beta = betas[i], I = Is))
    }
    
    # Remove the first row that are NA's
    df_signal <- df_signal[-1,]
    
    # Normalise the signals such that 1 corresponds to a 45deg surface angle and a
    # 5deg half cone angle, i.e. the current level of signal
    N <- df_signal %>% filter(beta == 5, psi == 45)
    df_signal %<>% mutate(I = I/N[["I"]])
    
    # Save the basic data frame to a text file
    df_signal %>% write_csv("aperture_signal_data.csv")
} else {
    #As the calculation takes a minute an alternative is to import previously
    #calculated data.
    
    df_signal <- read_csv("aperture_signal_data.csv", show_col_types = FALSE)
}
```


## Singnal plots

Create contour plots of the signal level and the signal to noise ratio. The
signal to noise ratio will be the $\propto \sqrt{I}$ because the dominant form
of noise is shot noise.

```{r, fig.width=2.354, fig.height=5}
df_signal %<>% mutate(SNR = sqrt(I))
df_signal %<>% mutate(SNR = if_else(is.nan(SNR), 0, SNR))

# Plot of the signal as a contour plot and heatmap
plt_contour <- df_signal %>%
    ggplot(aes(x = beta, y = psi)) +
    geom_raster(aes(fill = I), interpolate = TRUE) +
    geom_contour(aes(z = I), colour = "white", size = 0.5, binwidth = 10) +
    geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
    scale_fill_viridis() +
    scale_x_continuous(breaks = c(0,20,40,60,80,90)) +
    scale_y_continuous(breaks = c(0,20,40,60,80,100,120,140,160,180)) +
    coord_fixed(expand = FALSE) + 
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(expression("Surface angle/"*degree)) +
    labs(fill = "Signal") + 
    theme(text = element_text(size = 9), legend.position = "top")

print(plt_contour)
```

For the paper we compare the intensity change across $\psi$ for two different 
aperture sizes in order to demonstrate the extension of contrast due to partial
masking.

```{r, fig.width=3.287, fig.height=2.2}
df1 <- df_signal %>% filter(beta == 10) %>% mutate(I = I/max(I))
df2 <- df_signal %>% filter(beta == 45) %>% mutate(I = I/max(I))
df3 <- bind_rows(df1, df2)
df3 %<>% mutate(beta = as.factor(beta))

plt_options <- df3 %>% ggplot(aes(x = psi, y = I, colour = beta)) + 
  geom_line(linewidth=1) + 
#  scale_fill_manual(values = as.factor(c(10, 45)), labels = c(expression('10'*degree), expression('45'*degree))) +
  scale_colour_colorblind(name = 'β') + 
  labs(x = expression(psi*'/'*degree), y="Normalised intensity") +
  theme(legend.position = c(0.87, 0.73),
        text = element_text(size = 9),
        aspect.ratio = 2/(1+sqrt(5)))
plt_options
```

```{r}
if (save_tex) {
    plt_options <- plt_options + 
        xlab("$\\psi/^\\circ$") +
      scale_colour_colorblind(name = '$\\beta$')
      
    tikz("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/signal_aperture_size_line.tex", standAlone = FALSE, width = 3.278, height = 2.2)
    print(plt_options)
    dev.off()
}
```

Assuming shot noise the signal to noise ratio can be plotted as well: it is
simply the square route of the signal.

```{r, fig.width=2.354, fig.height=5}
# Plot of the signal to noise ratio as a contour plot and heatmap
plt_contour_SNR <- df_signal %>%
    ggplot(aes(x = beta, y = psi)) +
    geom_raster(aes(fill = SNR), interpolate = TRUE) +
    geom_contour(aes(z = SNR), colour = "white", size = 0.5, binwidth = 1) +
    geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
    scale_fill_viridis() +
    scale_x_continuous(breaks = c(0,20,40,60,80,90)) +
    scale_y_continuous(breaks = c(0,20,40,60,80,100,120,140,160,180)) +
    coord_fixed(expand = FALSE) + 
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(expression("Surface angle/"*degree)) +
    labs(fill = "SNR") + 
    theme(text = element_text(size = 9), legend.position = "top")

print(plt_contour_SNR)
```

Create a plot of the detected intensity with aperture size using aperture radius
instead of half cone angle. Assume a working distance of 3mm and a detection
angle of $45^\circ$.

```{r, fig.width=3, fig.height=2}
rs = seq(0, 2, by = 0.1)
I <- rep(0, length(rs))
for (i in seq(1, length(rs))) {
    I[i] = intensityRadius(45*pi/180, rs[i], 3)
}
I <- I/intensityRadius(45*pi/180, 0.5, 3)
df_signal2 <- tibble(rs, I)

plt_radius <- df_signal2 %>% ggplot(aes(x = rs, y = I)) +
    geom_line() + 
    geom_vline(aes(xintercept = 0.5), colour = colorblind_pal()(2)[2]) + 
    labs(x = "Aperture radius/mm", y = "Signal") + 
    theme(text = element_text(size = 9))

print(plt_radius)
```

### Save the plots

Save the contour plots as vector graphics (`.eps`) and as raster graphics (`.png`).

```{r}
if (save_plots) {
    ggsave("signal_aperture.eps", plt_contour, width = 2.354, height = 5)
    ggsave("SNR_aperture.eps", plt_contour_SNR, width = 2.354, height = 5)
    
    ggsave("signal_aperture.png", plt_contour, width = 2.354, height = 5)
    ggsave("SNR_aperture.png", plt_contour_SNR, width = 2.354, height = 5)
    
    ggsave("signal_aperture_mm.eps", plt_radius, width = 3, height = 2)
    ggsave("signal_aperture_mm.png", plt_radius, width = 3, height = 2)
    
    ggsave("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/signal_aperture_size_line.eps", plt_options, width = 3.287, height = 2.6)
    ggsave("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/signal_aperture_size_line.png", plt_options, width = 3.287, height = 2.6)
}
```

Export the contour plots as `.tex` files for improting into my thesis.

```{r message=FALSE, warning=FALSE}
if (save_tex) {
    plt_contour <- plt_contour + 
        xlab("Half cone angle/$^\\circ$") +
        ylab("Surface angle/$^\\circ$") +
        theme(text = element_text(size = 9))
    tikz("2Dplot.tex", standAlone = FALSE, width = 2.354, height = 5)
    print(plt_contour)
    dev.off()
        
    plt_contour_SNR <- plt_contour_SNR + 
        xlab("Half cone angle/$^\\circ$") +
        ylab("Surface angle/$^\\circ$") +
        theme(text = element_text(size = 9))
    tikz("2Dplot_SNR.tex", standAlone = FALSE, width = 2.354, height = 5)
    print(plt_contour_SNR)
    dev.off()
    
    tikz("signal_aperture_mm.tex", standAlone = FALSE, width = 3, height = 2)
    print(plt_radius)
    dev.off()
}
```


# Elliptical aperture

Is it better to have a circular aperture or an elliptical one. If an elliptical
one is a 'wide' or 'long' aperture better?

Use the ellipse integration to find out.


## Test the elliptical integral

First test the elliptical integral against the circular analytic formula to
check that it's working

```{r, fig.width=5, fig.height=3}
betas <- seq(1, 20)
I_circ <- rep(0, length(betas))
I_ellip <- rep(0, length(betas))
for (i in seq(1, length(betas))){ 
    I_circ[i] <- intensityAnl(45*pi/180, betas[i]*pi/180)
    I_ellip[i] <- intensityElliptical(45*pi/180, betas[i]*pi/180, betas[i]*pi/180)
}

df_ellipTest <- tibble(betas, I_circ, I_ellip)

plt_test <- df_ellipTest %>% pivot_longer(!betas, names_to = "Model", values_to = "I") %>% 
    ggplot(aes(x = betas, y = I, linetype = Model, colour = Model)) + 
    geom_line() + 
    scale_color_colorblind() + 
    theme(text = element_text(size = 9))

print(plt_test)
```


## Solid angle calculations

In order to compare contrast between the elliptical and circular shaped
apertures it is necessary to get an equivalence in solid angle for the whole
range of values. Do the calculation both for an aperture with the same solid
angle as the current design and one with double the solid angle.

```{r}
# Current solid angle
current_omega <- omegaEllipseBeta(10*pi/180, 10*pi/180)

# Range of angles in one of the dimensions
beta_a <- c(2, 3, 5, 10)

# Calculate the  values of the other half cone angle
beta_b <- rep(0, length(beta_a))
for (i in seq(1, length(beta_a))) {
    beta_tmp <- seq(1, 89, by=0.2)
    omegas <- rep(0, length(beta_tmp))
    for (j in seq(1, length(beta_tmp))) {
        omegas[j] <- omegaEllipseBeta(beta_a[i]*pi/180, beta_tmp[j]*pi/180)
    }
    tmp_fun <- approxfun(omegas, beta_tmp)
    beta_b[i] <- tmp_fun(current_omega)
}
```

```{r}
# Check the solid angles calculated
omegas <- rep(0, length(beta_a))
for (i in seq(1, length(beta_a))) {
    omegas[i] <- omegaEllipseBeta(beta_a[i]*pi/180, beta_b[i]*pi/180)
}
print("Fractional range of the resulting values:")
print(diff(range(omegas))/mean(omegas))

```

For a few specific ratios look at how the signal changes with the surface
orientation.

```{r, fig.width=2.354, fig.height=2.6, warning=FALSE}
df_elliptical <- tibble(beta_a=NA, beta_b=NA, psi=NA, I=NA)
psis <- seq(0, 90)
for (i in seq(1, length(beta_a))) {
    Is <- rep(0, length(psis))
    for (j in seq(1, length(Is))) {
        Is[j] <- intensityElliptical(psis[j]*pi/180, beta_a[i]*pi/180, beta_b[i]*pi/180)
    }
    df_elliptical <- bind_rows(df_elliptical, tibble(psi=psis, beta_a=beta_a[i], 
                                                     beta_b=beta_b[i], I = Is))
}

# Remove the first row that are NA's
df_elliptical <- df_elliptical[-1,]

df_elliptical %<>% mutate(aspect_ratio = beta_b/beta_a)

plt_elliptical <- df_elliptical %>% 
    mutate(aspect_ratio = as_factor(round(df_elliptical$aspect_ratio)),
           I = I/max(I)) %>%
    ggplot(aes(x = psi, y = I, colour = aspect_ratio))  + 
    geom_line() + 
    scale_color_colorblind() +
    labs(x = "$\\psi^\\circ$", y = "Relative signal") + 
    guides(colour=guide_legend(nrow=1)) +
    scale_x_continuous(breaks = c(0,20,40,60,80,90)) +
    xlim(0, 90) +
    ylim(c(0, 1)) +
    theme(legend.position = "top", 
          legend.title = element_blank(), 
          text = element_text(size = 9))

print(plt_elliptical)
```

## Partial masking with an elliptical detector

If there is partial masking then a Monte-Carlo method of integration has to be
used.

### MC test

Test the implemented Monte-Carlo methods against the quadrature integration method where they can both be applied (where partial masking does not occur). 

```{r}
psi <- seq(0, 110)
I <- rep(0, length(psi))
IMC <- rep(0, length(psi))
for (i in seq(1, length(psi))) {
    I[i] <- intensityElliptical(psi[i]*pi/180, 10*pi/180, 10*pi/180)
    IMC[i] <- intensityEllipticalMC(psi[i]*pi/180, 10*pi/180, 10*pi/180, 100000)
}
df_elliptical_tmp <- tibble(psi=psi, Int=I/max(I), MC=IMC/max(I))
```

```{r}
df_elliptical_tmp %>% pivot_longer(!psi, names_to = "Model", values_to = "signal") %>%
    ggplot(aes(x=psi, y=signal, colour=Model)) + 
    geom_line() + 
    scale_colour_colorblind() +
    ylim(0, 1)
```

The test shows that the models agree. Now either calculate or import the 
data for "long" apertuers where significant partial masking occurs.

```{r}
if (FALSE) {
    df_elliptical2 <- tibble(beta_a=NA, beta_b=NA, psi=NA, I=NA)
    psis <- seq(0, 135, by=1.5)
    for (i in seq(1, length(beta_a))) {
        Is <- rep(0, length(psis))
        for (j in seq(1, length(Is))) {
            Is[j] <- intensityEllipticalMC(psis[j]*pi/180, beta_b[i]*pi/180, beta_a[i]*pi/180, 10000000)
        }
        df_elliptical2 <- bind_rows(df_elliptical2, tibble(psi=psis, beta_a=beta_a[i], 
                                                         beta_b=beta_b[i], I = Is))
    }
    
    # Remove the first row that are NA's
    df_elliptical2 <- df_elliptical2[-1,]
    
    df_elliptical2 %<>% mutate(aspect_ratio = beta_b/beta_a)
    
    df_elliptical2 %>% write_csv("elliptical_long_data.csv")
} else {
    # Alternativly load the data from a data file because the computation takes time.
    df_elliptical2 <- read_csv("elliptical_long_data.csv", show_col_types = FALSE)
}
```

Plot of the 'long' apertures.

```{r, fig.width=2.354, fig.height=2.6}
plt_elliptical2 <- df_elliptical2 %>% 
    mutate(aspect_ratio = as_factor(round(aspect_ratio)),
           I = I/max(I)) %>%
    ggplot(aes(x = psi, y = I, colour = aspect_ratio))  + 
    #geom_line() + 
    geom_smooth(method = "loess", se=FALSE, span=0.2) + 
    scale_colour_colorblind() +
    labs(x = "$\\psi/^\\circ$", y = "Relative signal") +
    ylim(c(0, 1)) +
    theme(legend.position = "top", 
          legend.title = element_blank(), 
          text = element_text(size = 9))

print(plt_elliptical2)
```

### Plot for paper

This is a combination of both the long and wide apertures in a single figures for use in the paper.

```{r, fig.width=3.287, fig.height=4.5}
df_ell <-  bind_rows(Wide = df_elliptical, Long = df_elliptical2, .id = 'Type')
N <- max(df_ell['I'])

plt_ell <- df_ell %>% mutate(aspect_ratio = as_factor(round(aspect_ratio))) %>%
    ggplot(aes(x = psi, y = I/N, colour = aspect_ratio)) + 
    geom_smooth(method = "loess", se=FALSE, span=0.2, linewidth=1) + 
    facet_wrap(~Type, ncol = 1) + 
    scale_colour_colorblind(name = "Aspect ratio") +
    labs(x = "$\\psi/^\\circ$", y = "Relative signal") +
    ylim(c(0, 1)) +
    theme(legend.position = "top", 
          #legend.title = element_blank(), 
          text = element_text(size = 9),
          aspect.ratio = 2/(1+sqrt(5)))

plt_ell
```

## Save elliptical plots

There are two plots, one for "wide" apertures and the other for "long"
apertures.

```{r}
if (save_tex) {
    tikz("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/elliptical_apertures.tex", standAlone = FALSE, width = 3.287, height = 4.5)
    print(plt_ell)
    dev.off()
}
```

# Analyse contrast

## RMS and differential contrast to noise

Calculate both the RMS contrast to noise and the differential contrast to noise
for each value of beta. We use the 'standard SHeM configuration' of $\beta=10^\circ$
to normalise to 1.

Also calculate the equivalent signal increase assuming shot noise.

```{r}
beta_range <- c(0, 90)
betas <- seq(beta_range[1], beta_range[2], by = 1)

# Calculate the standard deviation and differential contrast for each value of beta
df_sigma <- tibble(beta = NA, contrast = NA, av = NA)
df_diff <- tibble(beta = NA, contrast = NA, av = NA)
for (i in seq(1, length(betas))) {
    df_oneBeta <- df_signal %>% filter(beta == betas[i], psi <= beta + 90)
    sig <- sd(df_oneBeta[["I"]])
    dif <- mean(abs(diff(df_oneBeta[["I"]])))
    av <- mean(df_oneBeta[["I"]])
    df_sigma %<>% add_row(beta = betas[i], contrast = sig, av = av)
    df_diff %<>% add_row(beta = betas[i], contrast = dif, av = av)
}
df_sigma <- df_sigma[-1,]
df_diff <- df_diff[-1,]

# RMS and differential contrast to noise
df_sigma %<>% mutate(CNR = contrast/sqrt(av))
df_diff %<>% mutate(CNR = contrast/sqrt(av))

# Normalise such that a value of 1 is the present aperture size
N1 <- (df_sigma %>% filter(beta == present_half_cone))[["CNR"]]
N2 <- (df_diff %>% filter(beta == present_half_cone))[["CNR"]]
df_sigma %<>% mutate(CNR = CNR/N1)
df_diff %<>% mutate(CNR = CNR/N2)

# Normalise the contrast too
N1 <- (df_sigma %>% filter(beta == present_half_cone))[["contrast"]]
N2 <- (df_diff %>% filter(beta == present_half_cone))[["contrast"]]
df_sigma %<>% mutate(contrast = contrast/N1)
df_diff %<>% mutate(contrast = contrast/N2)

# Combine the RMS and differential contrast to noise
df_contrast <- bind_rows("sigma" = df_sigma, "diff" = df_diff, .id = "method")

# Add the equivalent signal increase
df_contrast %<>% mutate(signal_increase = CNR^2)
```


We also consider 3 pairs of angles in order to calculate the difference to noise
for those specific angles: 
 - $(0^\circ,45^\circ)$
 - $(0^\circ,90^\circ)$
 - $(45^\circ,90^\circ)$

```{r}
# Calculate the Contrast to noise and difference to noise between 0/45, 0/90, 
# 45/90, for each beta
df_difference <- tibble(beta = NA, CNR = NA, I_0_45 = NA, I_0_90 = NA, 
                        I_45_90 = NA)
for (i in seq(1, length(betas))) {
    df_oneBeta <- df_signal %>% filter(beta == betas[i])
    I_0 <- (df_oneBeta %>% filter(psi == 0))[["I"]]
    I_45 <- (df_oneBeta %>% filter(psi == 45))[["I"]]
    I_90 <- (df_oneBeta %>% filter(psi == 90))[["I"]]
    df_difference %<>% add_row(beta = betas[i], CNR = "Difference", 
                               I_0_45 = I_0 - I_45,
                               I_0_90 = I_0 - I_90,
                               I_45_90 = I_45 - I_90)
    df_difference %<>% add_row(beta = betas[i], CNR = "DNR", 
                               I_0_45 = diffNoise(I_0, I_45),
                               I_0_90 = diffNoise(I_0, I_90),
                               I_45_90 = diffNoise(I_45, I_90))
}
df_difference <- df_difference[-1,]

# Normalise so that the current set up at a surface of 45deg has a value of 1
# for the difference between 0/45
N1 <- (df_difference %>% filter(beta == present_half_cone, 
                                CNR == "Difference"))[["I_0_45"]]
N2 <- (df_difference %>% filter(beta == present_half_cone, 
                                CNR == "DNR"))[["I_0_45"]]
df_difference %<>% mutate(
    I_0_45 = if_else(CNR == "Difference", I_0_45/N1, I_0_45/N2),
    I_0_90 = if_else(CNR == "Difference", I_0_90/N1, I_0_90/N2),
    I_45_90 = if_else(CNR == "Difference", I_45_90/N1, I_45_90/N2)
)
```

### Create plots

Plot the contast, CNR, and the equivalent signal increase. 

```{r, fig.width=3.287, fig.height=4}

# Plot of the RMS contrst to noise and the standard deviation
facet_names <- c(
    'CNR'="RMS contrast to noise",
    'contrast'="RMS contrast"
)
leg_labs <- list(
    'sigma'="RMS",
    'diff'="Differential"
)
cs = colorblind_pal()(4)

plt_CNR_sig <- df_contrast %>%
    gather(key = "variable", value = "value", -beta, -av, -method, -signal_increase) %>%
    filter(method == "sigma") %>%
    ggplot(aes(x = beta, y = value)) +
    geom_line(colour = cs[3], linewidth=1) + 
    geom_vline(aes(xintercept = present_half_cone), colour = cs[1],
               linewidth=1) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    facet_wrap( ~ variable, ncol = 1, scale = "free_y", 
               labeller = as_labeller(facet_names)) +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab("Normalised contrast") +
    theme(aspect.ratio = 2/(1+sqrt(5)),
          legend.position = "none",
          text = element_text(size=9))

print(plt_CNR_sig)

# Plot the required signal increase
plt_signal_increase <- df_contrast %>%
    filter(method == "sigma") %>%
    ggplot(aes(x = beta, y = signal_increase)) +
    geom_line(linewidth=1, , colour = cs[3]) + 
    geom_vline(aes(xintercept = present_half_cone), linewidth=1,colour = cs[1]) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab("Equivalent overall signal increase") +
    theme(aspect.ratio = 2/(1+sqrt(5)),
          legend.title = element_blank(),
          text = element_text(size=9))

print(plt_signal_increase)
```

And plot the 3 differences.

```{r, fig.width=3.287, fig.height=2.8}
# Plot the difference to noise and the difference
leg_labs <- list(
    bquote(0^degree * "," ~ 45^degree), 
    bquote(0^degree * "," ~ 90^degree),
    bquote(45^degree * "," ~ 90^degree)
)
plt_CNR_diff <- df_difference %>%
    gather(key = "pair", value = "value", -beta, -CNR) %>%
    ggplot(aes(x = beta, y = value, colour = pair)) + 
    geom_line(linewidth=1) +
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    scale_colour_colorblind(labels = leg_labs)  +
    facet_wrap( ~ CNR, ncol = 1, scale = "free_y") +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(NULL) +
    theme(legend.title = element_blank(),
          text = element_text(size=9),
          legend.position='top')

plt_DNR <- df_difference %>% 
    gather(key = "pair", value = "value", -beta, -CNR) %>%
    filter(CNR == "DNR") %>%
    ggplot(aes(x = beta, y = value, colour = pair)) +
    geom_line(linewidth=1) +
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    scale_colour_colorblind(labels = leg_labs)  +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab("Difference to noise ratio") +
    theme(legend.title = element_blank(),
          text = element_text(size=9),
          legend.position='top',
          aspect.ratio = 2/(1+sqrt(5)))

print(plt_CNR_diff)
print(plt_DNR)
```


### Save the contrast figures

```{r}
if (save_tex) {
    plt_signal_increase <- plt_signal_increase + labs(x = "Half cone angle/$^\\circ$")
    tikz("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/signal_increase.tex", standAlone = FALSE, width = 3.287, height = 2.2)
    print(plt_signal_increase)
    dev.off()

    plt_CNR_sig <- plt_CNR_sig + labs(x = "Half cone angle/$^\\circ$")
    tikz("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/RMS_contrast_to_noise.tex", standAlone = FALSE, width = 3.287, height = 4)
    print(plt_CNR_sig)
    dev.off()
}
```

# Pumping

We consider the pumping back out of the detector aperture. The back pumping can
either be modelled as an orifice,
$$
C_O = 11.6FA
$$
or as a cone
$$
C_A = \frac{4}{3}\pi V_m\frac{R_0^2\,R_k^2\,k}{(R_0 + R_k)L}
$$
$$
	\gamma = \frac{C_A}{C_R} = 1 + \frac{16}{3}k\,\tan\alpha
$$
where it is $C_R$ that is of current interest.

To calculate the conductance of the cone some parameters are used. These are the standard parameters for the Cambridge SHeM. 
 - $L$, the length of the cone to the stagnation region. 14mm in 'new chamber' configuration.
 - $R_k$, the radius of the large end of the cone. ???

We must also be able to calculate the other two .

`df_contrast` contains information on the equivalent signal increase for 
different values of beta. Create an interpolation function for that to calculate
the signal increase 


```{r}
# Pumping ratios giving effect on signal.
p <- function(Cd, Cb) Cd/(Cd + Cb)

# A function that gives the equivalent signal increase
df_tmp <- df_contrast %>% filter(method == 'sigma')
equiv_increase <- approxfun(df_tmp$beta, df_tmp$signal_increase)

cone_tmp <- function(beta, working_dist) {
    #TODO: double check this against the CAD
    Rk <- 3.6 # For all new designs in the 'new chamber' configuration 
    L <- 15.6 # for the 'new chamber' configuration
    
    R0 <- working_dist*tan(beta*pi/180)
    alpha <- atan((Rk - R0)/L)*180/pi 
    coneConductance(R0, Rk, L, alpha)
}

# Data frame
df_pumping <- tibble(beta = rep(seq(0,45), times = length(working_dists)),
                    working_dist = rep(working_dists, each = length(seq(0,45))))


# Calculate the pumping for the two methods 
df_pumping %<>% mutate(aperture = apertureConductance(beta, working_dist))
df_pumping %<>% mutate(cone = cone_tmp(beta, working_dist))

df_pumping %>% pivot_longer(c('aperture', 'cone'), names_to="method", values_to = "conductance") %>%
  filter(working_dist == 0.5) %>%
  ggplot(aes(x = beta, y = conductance, colour = method)) +
  geom_line()

#TODO: I think the cone formula breaks down at some point.... check it
#TODO: the units are completely off too.....
```
```{r}
# Pumping conductances for the two methods
df_3 <- df_pumping %>% filter(working_dist > 2.99 & working_dist < 3.01)
df_1 <- df_pumping %>% filter(working_dist > 0.99 & working_dist < 1.01)
```

Consider the ratio of pumping in a more abstract way.

```{r}

Cb <- seq(0.01, 3, by=0.01)
df <- tibble(Cb = Cb, Cd=1)
df %<>% mutate(p = p(Cd, Cb))

df %>% ggplot(aes(x=Cb, y=p)) + 
  geom_line() + 
  ylim(0, 1) + 
  labs(x='C_b/C_d', y='Proportion of siganl detected') 
```

```{r}
# TODO: this uses a different definition of sigma_calc()...     
# Calculate the standard deviation and the RMS contrast to noise
#df_pumping %<>% mutate(
#     sigma = df_contrast %>% sigma_calc(beta),
#     av = df_contrast %>% av_calc(beta)
#)
#df_pumping %<>% mutate(
#     sigma = sigma*pump_ion/(pump_ion + pumping),
#     av = av*pump_ion/(pump_ion + pumping),
#     CNR_sigma = sigma/sqrt(av)
#)
 
# Normalise such that a value of 1 is the present aperture size
#N <- (df_pumping %>% filter(beta == present_half_cone, 
#     abs(working_dist - present_working_dist) < 0.0001))[["CNR_sigma"]]
#df_pumping %<>% mutate(CNR_sigma = CNR_sigma/N)
 
# Add the equivalent signal increase
#df_pumping %<>% mutate(signal_increase = CNR_sigma^2)
```


```{r}
leg_labs <- list(
    "0$^\\circ$,45$^\\circ$", 
    "0$^\\circ$,90$^\\circ$",
    "45$^\\circ$,90$^\\circ$"
)

plt_DNR <- plt_DNR + scale_colour_colorblind(labels = leg_labs) + 
  labs(x = "Half cone angle/$^\\circ$")
tikz("C:/Users/SamLambrick/Documents/SMF_research_work/figure_making_reports/constrast-to-noise-analytic/difference_to_noise.tex", standAlone = FALSE, width = 3.287, height = 2.8)
print(plt_DNR)
dev.off()
```


```{r}
# Plot of the contrast to noise with the pumping taken into account
facet_names <- c(
    'CNR_sigma'="RMS contrast to noise",
    'sigma'="Standard deviation"
)
plt_CNR_pumping <- df_pumping %>%
    filter(working_dist == 3) %>%
    gather(key = "variable", value = "value", -beta, -av, -signal_increase) %>%
    ggplot(aes(x = beta, y = value)) +
    geom_line(colour = colorRampPalette(solarized_pal()(8))(1)) + 
    geom_vline(aes(xintercept = present_half_cone)) +
    scale_x_continuous(breaks = c(0,20,40,60,80)) +
    facet_wrap( ~ variable, ncol = 2, scale = "free_y", labeller = as_labeller(facet_names)) +
    xlab(expression("Half cone angle/"*degree)) + 
    ylab(NULL) +
    theme(aspect.ratio = 2/(1+sqrt(5)))

# Plot the equivalent signal increase
plt_signal_increase_pumping <- df_pumping %>%
     filter(working_dist == 3) %>%
     ggplot(aes(x = beta, y = signal_increase)) +
     geom_line(colour = colorRampPalette(solarized_pal()(8))(1)) + 
     geom_vline(aes(xintercept = present_half_cone)) +
     scale_x_continuous(breaks = c(0,20,40,60,80)) +
     xlab(expression("Half cone angle/"*degree)) + 
     ylab("Equivalent overall signal increase") +
     theme(aspect.ratio = 2/(1+sqrt(5)))
 
     
# Remove the NaNs for plotting
df_pumping[is.na(df_pumping)] <- 0
 
# Plot of the signal improvment as a function of both half cone angle and the
# working distance.
plt_contour_pumping <- df_pumping %>%
     ggplot(aes(x = beta, y = working_dist)) +
     geom_raster(aes(fill = signal_increase), interpolate = TRUE) +
    geom_contour(aes(z = signal_increase), colour = "white", size = 0.5, binwidth=1) +
     geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
     geom_hline(aes(yintercept = present_working_dist), colour = "firebrick1") +
     scale_fill_viridis() +
     coord_cartesian(expand = FALSE) + 
     xlab(expression("Half cone angle/"*degree)) + 
     ylab(expression("Working distance/mm")) +
     labs(fill = "Equivalent signal\nincrease")
 
# Plot of the RMS CNR as a function of both half cone angle and the
# working distance.
 plt_contour_pumpingCNR <- df_pumping %>%
     ggplot(aes(x = beta, y = working_dist)) +
     geom_raster(aes(fill = CNR_sigma), interpolate = TRUE) +
     geom_contour(aes(z = CNR_sigma), colour = "white", size = 0.5, binwidth=1) +
     geom_vline(aes(xintercept = present_half_cone), colour = "firebrick1") +
     geom_hline(aes(yintercept = present_working_dist), colour = "firebrick1") +
     scale_fill_viridis() +
     coord_cartesian(expand = FALSE) + 
     xlab(expression("Half cone angle/"*degree)) + 
     ylab(expression("Working distance/mm")) +
     labs(fill = "CNR")
```


